Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-04 paper/paper.tex
updated chart

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}

@@

\section{Related Work}
DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing %\cite{potts2011}. A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.

\section{Method}
\subsection{Corpus creation}
By accessing the Twitter "Firehose" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets. This provides us a smaller set of features in the overall corpus. The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
...\\

@@

A computer-posted spam tweet:
\begin{quote}
I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
\end{quote}

A retweet, signified by "RT":
\begin{quote}
RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
\end{quote}

We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
Data sets and scripts used for processing text data are available on the project website.\\

@@

We do all machine learning with the Mallet%\cite{McCallumMALLET} library developed by the University of Massachusetts. Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format. We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification. Not every Pipe proved to increase accuracy--some decreased it. We present the descriptions of and motivations for these Pipes here.

@@

@@

\begin{quote}
Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
I just poured apple juice on my cereal.. Gah. \#SoTired 
I hate Siri.. -\_\_\_- 
\end{quote}

@@

Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
\begin{quote}
Now on my iphone ?? http://t.co/Rqr1RL2R 
\end{quote}

@@

\begin{quote}
I listen to my iPod every day and it's just broke omg:(!!
\end{quote}

@@

After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings. As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set. In the following tweet, "loooool" is normalized to "loool".
\begin{quote}
\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C 
\end{quote}

@@

\section{Results}
...baseline using priors
  baseline using whitespace splitting in naive bayes.
  select interesting improvements.
  graphs of both validation types
  most useful features for classification

@@

@@

\section{ Acknowledgments}
Thank you to Dr. Jin Tian and our TA Ru He for their guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.

\bibliographystyle{plain}
\bibliography{paper}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}
\usepackage[round]{natbib}
\usepackage{graphicx}

@@

\section{Related Work}
DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing \cite{potts2011}. A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.

\section{Method}
\subsection{Corpus creation}
By accessing the Twitter \"Firehose\" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets. This provides us a smaller set of features in the overall corpus. The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
...\\

@@

A computer-posted spam tweet:
\begin{table}[h]
\centering
\begin{tabular}{|l|}
	\hline
	I've collected 10,650 gold coins! \\ http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
	\hline
\end{tabular}
\end{table}

A retweet, signified by "RT":
\begin{table}[h]
\centering
\begin{tabular}{|l|}
	\hline
	RT @PHILerNotebook: Trying to fix my Mac. \\ This gray loading bar takes 10 minutes to start up. \\ Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
	\hline
\end{tabular}
\end{table}

We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
Data sets and scripts used for processing text data are available on the project website. (http://tweets.curtisullerich.com/)\\

@@

We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}. Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format. We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification. Not every Pipe proved to increase accuracy--some decreased it. We present the descriptions of and motivations for these Pipes here.

@@

\begin{figure*}[t!]
\centering
\includegraphics[height=7cm]{chart}
\caption{Accuracy Chart}
\label{fig:chart}
\end{figure*}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|}
	\hline
	Cool ranch , 4 berry sundae , apple juice \#yessuh \\ \#latenight \#snack http://t.co/ttc3vujp \\ \hline
	I just poured apple juice on my cereal.. Gah. \#SoTired \\ \hline
	I hate Siri.. -\_\_\_- \\
	\hline
\end{tabular}
\caption{Examples of difficult tokenizations}
\label{tab:tokenization_examples}
\end{table}

@@

Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
\begin{quote}
\textit{Now on my iphone ?? http://t.co/Rqr1RL2R}
\end{quote}

@@

\begin{quote}
\textit{I listen to my iPod every day and it's just broke omg:(!!}
\end{quote}

@@

After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings. As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set. In the following tweet, "loooool" is normalized to "loool".
\begin{quote}
\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C 
\end{quote}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas vulputate ultricies lorem, quis consectetur erat tristique id. Nulla eget nunc in urna vestibulum ornare ac sed purus. Curabitur consequat gravida turpis in rutrum. Nulla vehicula condimentum luctus. Nam venenatis facilisis orci sed ullamcorper. In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum. Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero. Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis. Aliquam vitae leo sem. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Etiam consequat ante eu turpis molestie vel gravida felis varius. Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat. Aenean sit amet dui vel urna pretium dictum nec sed elit. Vivamus feugiat dictum neque imperdiet ultrices. Nullam commodo rhoncus elit id adipiscing. Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.

Integer dictum tristique felis vitae lobortis. Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl. Nullam vehicula magna convallis odio semper vestibulum. Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros. Nam tempor felis eget dui laoreet vehicula. Praesent imperdiet hendrerit elit sed tempus. Phasellus feugiat pretium metus id scelerisque. Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue. Donec pharetra molestie euismod. Nulla porttitor feugiat purus, in egestas lorem venenatis sed. Phasellus quis interdum diam. Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio. Vestibulum et nisl sodales quam commodo laoreet. Ut a tortor tortor.

\section{Results}

...baseline using priors
  baseline using whitespace splitting in naive bayes.
  select interesting improvements.
  graphs of both validation types
  most useful features for classification

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas vulputate ultricies lorem, quis consectetur erat tristique id. Nulla eget nunc in urna vestibulum ornare ac sed purus. Curabitur consequat gravida turpis in rutrum. Nulla vehicula condimentum luctus. Nam venenatis facilisis orci sed ullamcorper. In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum. Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero. Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis. Aliquam vitae leo sem. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Etiam consequat ante eu turpis molestie vel gravida felis varius. Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat. Aenean sit amet dui vel urna pretium dictum nec sed elit. Vivamus feugiat dictum neque imperdiet ultrices. Nullam commodo rhoncus elit id adipiscing. Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.

Integer dictum tristique felis vitae lobortis. Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl. Nullam vehicula magna convallis odio semper vestibulum. Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros. Nam tempor felis eget dui laoreet vehicula. Praesent imperdiet hendrerit elit sed tempus. Phasellus feugiat pretium metus id scelerisque. Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue. Donec pharetra molestie euismod. Nulla porttitor feugiat purus, in egestas lorem venenatis sed. Phasellus quis interdum diam. Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio. Vestibulum et nisl sodales quam commodo laoreet. Ut a tortor tortor.

Phasellus et mi eu est fermentum cursus id sodales nisi. Maecenas sodales ornare mauris, nec cursus mi commodo non. In pulvinar odio id est pharetra cursus. Fusce blandit scelerisque bibendum. Aliquam erat volutpat. Aliquam tellus lorem, pharetra a vehicula nec, tincidunt sit amet felis. Nullam nec sapien quis leo facilisis commodo at vel enim. Suspendisse ultricies massa at nisl iaculis scelerisque. Phasellus sed sodales augue. Pellentesque a nisl enim.

Mauris at eros velit, non venenatis augue. Fusce vel ornare purus. Praesent condimentum lectus sit amet sem ullamcorper eget euismod tellus dapibus. Aenean fringilla urna vel nisl accumsan imperdiet. Duis cursus mattis molestie. Phasellus est lorem, condimentum quis congue eget, condimentum scelerisque arcu. Phasellus odio lacus, imperdiet at convallis et, vehicula a nisi. Mauris consequat urna vitae ipsum vulputate ullamcorper. Fusce ullamcorper mauris dolor. Quisque gravida hendrerit tristique. Fusce magna urna, vestibulum eget condimentum eu, semper sit amet felis. Ut placerat hendrerit neque id vestibulum. Phasellus convallis, nulla at fermentum bibendum, massa risus tempus eros, et malesuada diam enim sed purus. Praesent tincidunt dapibus lobortis. Curabitur sodales dignissim est quis tempus.

Aenean vel enim eu mauris scelerisque pulvinar in quis odio. Suspendisse eu sapien vitae eros ultrices congue volutpat quis elit. Aliquam nisl nibh, hendrerit ut feugiat eget, gravida eget urna. In nisl felis, elementum ut sollicitudin non, fringilla in neque. Aliquam quis luctus lacus. Cras et mauris sem, vel imperdiet sapien. Suspendisse in ligula id turpis adipiscing sodales vitae ut lectus. Vestibulum neque nulla, commodo vitae venenatis id, accumsan vitae odio. Quisque velit purus, tempor non porta laoreet, elementum vel sem. Nullam mollis euismod dolor, eget pulvinar elit cursus eget. Nunc quis pharetra odio. Donec lacus leo, pulvinar quis vestibulum eget, porta id nibh.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Maecenas vulputate ultricies lorem, quis consectetur erat tristique id. Nulla eget nunc in urna vestibulum ornare ac sed purus. Curabitur consequat gravida turpis in rutrum. Nulla vehicula condimentum luctus. Nam venenatis facilisis orci sed ullamcorper. In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum. Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero. Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis. Aliquam vitae leo sem. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Etiam consequat ante eu turpis molestie vel gravida felis varius. Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat. Aenean sit amet dui vel urna pretium dictum nec sed elit. Vivamus feugiat dictum neque imperdiet ultrices. Nullam commodo rhoncus elit id adipiscing. Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.

Integer dictum tristique felis vitae lobortis. Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl. Nullam vehicula magna convallis odio semper vestibulum. Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros. Nam tempor felis eget dui laoreet vehicula. Praesent imperdiet hendrerit elit sed tempus. Phasellus feugiat pretium metus id scelerisque. Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue. Donec pharetra molestie euismod. Nulla porttitor feugiat purus, in egestas lorem venenatis sed. Phasellus quis interdum diam. Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio. Vestibulum et nisl sodales quam commodo laoreet. Ut a tortor tortor.

@@

\section{ Acknowledgments}
Thank you to Dr. Jin Tian and our class teaching assistant, Ru He, for their helpful guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.

\bibliographystyle{plainnat}
\bibliography{paper}
